\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-03-28 Latex/paper-resum.tex
Changes Abstract/Conclusions
Changes in the Abstract and the conclusions. Change on the last figure's position.

\title{\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}}

@@

\maketitle
\begin{abstract}
AA
\end{abstract}
%\keywords{V--}
%\ccode{MSC classification}{--}
%\ccode{JEL classification}{--}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order.jpg}
	\end{center}
	\caption{Convexity Mc Vs Convexity Malliavin}
	\label{fig:CMS}
\end{figure} 
\end{example}

\section{Conclusions}\label{sec:Conclusion}
In the present paper, we have shown how we can use Malliavin calculus to find the convexity adjustment for several typical interest rate products. We have seen, that Malliavin calculus provides us with a simple way to get a template for the convexity adjustment of several products under a general Cheyette model dynamic with one factor. The method is extrapolated with little effort to a Cheyette model with stochastic volatility, or even a  Cheyette model with several factors. We have also seen, the good accuracy of the formulas that we have got using this method.

>>>>

\title{\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}}

@@

\maketitle
\begin{abstract}
In this paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products. Malliavin calculus provides a simple way to get a template for the convexity adjustment. We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model. We have also seen the excellent quality of the numerical accuracy of the formulas obtained.
\end{abstract}
%\keywords{V--}
%\ccode{MSC classification}{--}
%\ccode{JEL classification}{--}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order.jpg}
	\end{center}
	\caption{Convexity Mc Vs Convexity Malliavin}
	\label{fig:CMS}
\end{figure} 
\end{example}

\section{Conclusions}\label{sec:Conclusion}
In the present paper, we develop a novel method based on the Malliavin calculus to find an approximation for the convexity adjustment for various classical interest rate products. Although the convexity adjustment could be calculated using other techniques, Malliavin calculus provides a simple way to get a template for the convexity adjustment. We find the approximation for Futures, OIS Futures, FRAs, and CMSs under a general family of the one-factor Cheyette model. We have also seen the excellent quality of the numerical accuracy of the formulas obtained.

In future work, the methodology could be extrapolated to a Cheyette model with stochastic volatility or even to a model with several factors.
